Multispecies survey for diet comp

### 2020-11-20 SurveyDietCompTest.Rmd
renaming for consistency

The current partial `sample_diet()` function needs to change because it expects a wide format file of diet proportions, rather than a long-format file of consumption in tons which is the output of `create_survey_diet()`.

@@

The current function removes predators not expected on a fish trawl survey, removes prey types that are normally not counted, then adds uniform error to half the remaining diet proportions, removes a random subet of prey accounting for <0.25 diet proportion, then renormalizes. I would rather have a function that could be used on any "survey" so have already removed hardcoded predator selection. I think also the distributional assumptions need revision; a Dirichlet is most appropriate to simulate continuous proportions.

@@

@@

@@

# global proportion diet comp for comparison with survey_cons
diettest <- load_diet_comp(here("atlantisoutput", "NOBA_march_2020"), 
                           "nordic_runresults_01DietCheck.txt", fgs = fgs) %>%
  filter(atoutput>0)

>>>>

The intial partial `sample_diet()` function in `atlantisom` needs to change because it expects a wide format file of diet proportions, rather than a long-format file of consumption in tons which is the output of `create_survey_diet()`.

@@

The initial function removed predators not expected on a fish trawl survey, removed prey types that are normally not counted, then adds uniform error to half the remaining diet proportions, removes a random subet of prey accounting for <0.25 diet proportion, then renormalizes. I would rather have a function that could be used on any "survey" so have already removed hardcoded predator selection.

I think also the distributional assumptions need revision; a Dirichlet is most appropriate to simulate continuous proportions. See [Douma and Weedon 2019](https://besjournals.onlinelibrary.wiley.com/doi/10.1111/2041-210X.13234) for an excellent overview, as well as [a description of the Dirichlet alpha parameter](https://stats.stackexchange.com/questions/244917/what-exactly-is-the-alpha-in-the-dirichlet-distribution) and [Lin 2016](https://mast.queensu.ca/~communications/Papers/msc-jiayu-lin.pdf).

Here I'll use the random number generation function `rdirichlet()` in the package `DirichletReg`but others may work too.

# global proportion diet comp for comparison with survey_cons
diettest <- load_diet_comp(here("atlantisoutput", "NOBA_march_2020"), 
                           "nordic_runresults_01DietCheck.txt", fgs = fgs) %>%
  filter(atoutput>0) %>%
  filter(species %in% survspp)

@@

dat <- survey_cons
#dat <- diettest

@@

    # rename to match output of load_diet_comp
    names(dat2)[names(dat2) == 'dietprop'] <- 'atoutput'
    names(dat2)[names(dat2) == 'time'] <- 'time.days'

  } else dat2 <- dat

@@
